### 2009-12-17 doc/tech_doc/infosys/infosys_technical.tex
Fixed bibliography

\textit{This section extensively uses terms defined in "Security Framework of WS-ARC" document"~\cite{arcsec}.}

@@

Those 3 action groups are handled using Security Framework of ARC~\cite{arcsec}. For each group a corresponding
Action is defined for the ARC policy language as described in table \ref{tab:policy_actions}.

@@

\textit{For information about sophisticated authorization policies and how to deploy various Policy Decision Point entities please see "Security Framework of WS-ARC" document"~\cite{arcsec}.}

@@

In order to activate the policy it must be linked to the ISIS service through the Security Handle and the Policy 
Decision Point emedded into the configuration of ISIS. Below is a minimal example configuration element of 
an ISIS service. In lines 7--17 a set of Security Handlers and Policy Decision Points is configured to handle
policies written in the ARC Policy Language (described in ~\cite{arcsec}). Line 14 specifies that the policy is 
read from file \textit{/opt/arc/etc/isis/policy.xml} every time a new request arrives. If the policy is not 
satisfied then the ISIS returns SOAP Fault instead of the usual informative response.

>>>>

\textit{This section extensively uses terms defined in "ARC Security Framework (NORDUGRID-TECH-16)" document"~\cite{arc1-security}.}

@@

Those 3 action groups are handled using Security Framework of ARC~\cite{arc1-security}. For each group a corresponding
Action is defined for the ARC policy language as described in table \ref{tab:policy_actions}.

@@

\textit{For information about sophisticated authorization policies and how to deploy various Policy Decision Point entities please see "ARC Security Framework (NORDUGRID-TECH-16)" document"~\cite{arc1-security}.}

@@

In order to activate the policy it must be linked to the ISIS service through the Security Handle and the Policy 
Decision Point emedded into the configuration of ISIS. Below is a minimal example configuration element of 
an ISIS service. In lines 7--17 a set of Security Handlers and Policy Decision Points is configured to handle
policies written in the ARC Policy Language (described in~\cite{arc1-security}). Line 14 specifies that the policy is
read from file \textit{/opt/arc/etc/isis/policy.xml} every time a new request arrives. If the policy is not 
satisfied then the ISIS returns SOAP Fault instead of the usual informative response.
